### 2019-10-17 README.Rmd
Add roxygen2 to packrat

**Text and figures:** [CC-BY-NC-SA-4.0](http://creativecommons.org/licenses/by-nc-sa/4.0/).

@@

**Datasets:** [CC-BY-NC-SA-4.0](http://creativecommons.org/licenses/by-nc-sa/4.0/).

>>>>

**Text and figures:** [CC-BY-SA-4.0](http://creativecommons.org/licenses/by-sa/4.0/).

@@

**Datasets:** [CC-BY-SA-4.0](http://creativecommons.org/licenses/by-sa/4.0/).
